Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/report.tex
Including all appendices now

\begin{abstract}
MSc in Software Engineering and Internet Architecture 2016

Improving content discovery through combining linked data and data mining techniques

By Ross Fenning

Project Supervisor: Dr. D. Thakker

An comparative study of multiple approaches for extracting linked data
from web content published by the BBC for the purposes of applying
machine learning to cluster related content.

@@

\chapter{Proposal}
\chapter{Ethics Form}
\includepdf[pages=1-4]{ethics.pdf}
\chapter{Summary}

>>>>

\begin{abstract}
\noindent MSc in Software Engineering and Internet Architecture 2016\\
\vspace{5mm}
\noindent Improving content discovery through combining linked data and data mining techniques\\
\vspace{5mm}
\noindent By Ross Fenning\\
\vspace{5mm}
\noindent Project Supervisor: Dr. D. Thakker\\
\vspace{5mm}
\vspace{5mm}
\noindent A comparative study of multiple approaches for extracting linked data
from web content published by the BBC for the purposes of applying
machine learning to cluster related content.

@@

\chapter{Proposal}
\includepdf{../proposal/proposal.pdf}
\chapter{Ethics Form}
\includepdf[pages=1-4]{ethics.pdf}
\chapter{Summary}
\includepdf{../paper/paper.pdf}
